---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# harmonydata

<!-- badges: start -->

<!-- badges: end -->

The goal of harmonydata is to ...

## Getting started with the Harmony R library

### Installing R library

You can install the development version of harmonydata from [GitHub](https://github.com/harmonydata/harmony_r) with:

``` r
# install.packages("devtools")
devtools::install_github("harmonydata/harmony_r")
```

## Parsing a raw file into an Instrument

If you want to read in a raw (unstructured) PDF or Excel file, you can do this via a POST request to the REST API. This will convert the file into an Instrument object in JSON.It returns the instrument as a list.

```{r example}
library(harmonydata)
instrument = load_instruments_from_file(path = "examples/GAD-7.pdf")
instrument

```

You can also input a url containing the questionnaire.

```{r}
instrument_2 = load_instruments_from_file("https://medfam.umontreal.ca/wp-content/uploads/sites/16/GAD-7-fran%C3%A7ais.pdf") 
instrument_2
```

## Matching instruments

You can get a list containing the results of the match.

```{r}
instruments = append(instrument, instrument_2)
match = match_instruments(instruments)
match
```
