---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Harmony R library: harmonydata

## Getting started with the Harmony R library

* Check out [this video walkthrough](https://www.youtube.com/watch?v=hFqg6T_BqZc&t=1s) installing and running R on Windows 10.

* You can run the walkthrough Python notebook in [Google Colab](https://colab.research.google.com/github/harmonydata/harmony/blob/main/Harmony_example_walkthrough.ipynb) with a single click: <a href="https://colab.research.google.com/github/harmonydata/harmony/blob/main/Harmony_example_walkthrough.ipynb" target="_parent"><img src="https://colab.research.google.com/assets/colab-badge.svg" alt="Open In Colab"/></a>

* You can also download an R markdown notebook to run in R Studio: <a href="https://harmonydata.ac.uk/harmony_r_example.nb.html" target="_parent"><img src="https://img.shields.io/badge/RStudio-4285F4" alt="Open In R Studio"/></a>

* You can run the walkthrough R notebook in Google Colab with a single click: <a href="https://colab.research.google.com/github/harmonydata/experiments/blob/main/Harmony_R_example.ipynb" target="_parent"><img src="https://colab.research.google.com/assets/colab-badge.svg" alt="Open In Colab"/></a>

* [View the PDF documentation of the R package on CRAN](https://cran.r-project.org/web/packages/harmonydata/harmonydata.pdf)



### Installing R library

You can install the development version of harmonydata from [GitHub](https://github.com/harmonydata/harmony_r) with:

```{r}
#install.packages("devtools") # If you don't have devtools installed already.
library(devtools)
devtools::install_github("harmonydata/harmony_r")
```

## Setting up domain

Before starting, you can set up the remote API endpoint for harmony using this function. By default it uses the remote Harmony API [https://api.harmonydata.ac.uk](https://api.harmonydata.ac.uk){.uri}



```{r}
harmonydata::set_url()
```

For example, if you want to use Harmony locally, you can run the [Harmony API as a Docker container](https://github.com/harmonydata/harmonyapi). By default it runs on localhost at port 8000. In this case you can run this command to run it locally:

```{bash}
docker run -p 8000:8000 harmonydata/harmonylocal
```

Now in R you can set the R library to point to your local Harmony on Docker.

```{r}
harmonydata::set_url("http://localhost:8000")
```

## Parsing a raw file into an Instrument

If you want to read in a raw (unstructured) PDF or Excel file, you can do this via a POST request to the REST API. This will convert the file into an Instrument object in JSON.It returns the instrument as a list.

```{r example}
library(harmonydata)
instrument = load_instruments_from_file(path = "examples/GAD-7.pdf")
names(instrument[[1]])

```

You can also input a url containing the questionnaire.

```{r}
instrument_2 = load_instruments_from_file("https://medfam.umontreal.ca/wp-content/uploads/sites/16/GAD-7-fran%C3%A7ais.pdf") 
names(instrument_2[[1]])
```

## Matching instruments

You can get a list containing the results of the match.Here we can see a list of similarity score for each question comapred to all the other questions in th other questionaire.

```{r}
instruments = append(instrument, instrument_2)
match = match_instruments(instruments)
names(match)
```

Here is how the matches look like.

```{r}

match$matches
```

# Running harmonydata locally from a docker image

To run harmonydata locally, first you need to pull the docker image using the terminal.

## 1. Pull docker image

``` shell
docker pull harmonydata/harmonyapi
```

## 2. Run docker image

``` shell
docker run -p 8000:80 harmonyapi
```

## 3. Configure harmonydata to run locally

Set url to use localhost. Don't forget to expose port 8000:

```{r}
set_url(harmony_url = "http://localhost:8000")
```


## 📜 How do I cite Harmony?

You can cite our validation paper:

 McElroy, Wood, Bond, Mulvenna, Shevlin, Ploubidis, Scopel Hoffmann, Moltrecht, [Using natural language processing to facilitate the harmonisation of mental health questionnaires: a validation study using real-world data](https://bmcpsychiatry.biomedcentral.com/articles/10.1186/s12888-024-05954-2#citeas). BMC Psychiatry 24, 530 (2024), https://doi.org/10.1186/s12888-024-05954-2
 

A BibTeX entry for LaTeX users is

{{< rawhtml >}}
<pre>
@article{mcelroy2024using,
  title={Using natural language processing to facilitate the harmonisation of mental health questionnaires: a validation study using real-world data},
  author={McElroy, Eoin and Wood, Thomas and Bond, Raymond and Mulvenna, Maurice and Shevlin, Mark and Ploubidis, George B and Hoffmann, Mauricio Scopel and Moltrecht, Bettina},
  journal={BMC psychiatry},
  volume={24},
  number={1},
  pages={530},
  year={2024},
  publisher={Springer}
}
</pre>
{{< /rawhtml >}}

